\documentclass{e85}

\ps{6}
\date{2019}
\author{}
\coauthor{}

\begin{document}
\begin{enumerate}
\item Number Systems
  \begin{enumerate}
  \item Write \(-9.0625\) as a 12-bit fixed-point number with 7
    integer and 5 fractional bits.
    \begin{solution}
    \end{solution}
  \item Compute the sum of the following IEEE single-precision numbers
    by hand.
    \[
      \mathrm{0x41200000} + \mathrm{0x40D80000}
    \]
    \begin{solution}
    \end{solution}
  \end{enumerate}

\item Building Blocks

  You need to blink 27 LEDs in a mesmerizing pattern to create a nifty
  display for the next Hackathon.  You want to generate the pattern
  with a microcontroller that only has two free pins available.
  Design some hardware that could go on a breadboard to receive inputs
  from these two pins and control the LEDs.  Assume you have any
  reasonable gates, registers, and other building blocks available.
  \begin{solution}
  \end{solution}

\item FPGA Configuration

  How many Altera Cyclone IV logic elements (LEs) are required to
  build each of the following functions?  Explain.
  \begin{enumerate}
  \item 2-input OR
    \begin{solution}
    \end{solution}
  \item 8-input AND
    \begin{solution}
    \end{solution}
  \item arbitrary FSM with 3 states, 1 input and 1 output
    \begin{solution}
    \end{solution}
  \item 8-bit counter with reset and enable
    \begin{solution}
    \end{solution}
  \end{enumerate}

\item Datasheets

  Answer the following questions to familiarize yourself with the
  STM32F042K6T6 microcontroller that we will be using.  See the
  STM32F042x4 Datasheet on the class web pae.  For each question, note
  the page number and symbol for the specification that informs your
  answer.
  \begin{enumerate}
  \item What is the range of allowable digital supply voltages for
    normal operation?
    \begin{solution}
    \end{solution}
  \item If you accidentally connect a \SI{5}{\V} supply to the
    \(V_{DD}\), should you expect it to survive?
    \begin{solution}
    \end{solution}
    For the remainder of this question, assume \SI{3.3}{\V} operation.
  \item What is the typical \(V_{DD}\) power consumption in normal
    operating mode at \(f_c = \SI{48}{\MHz}\) with all features
    running full-bore?  How long could the chip run off a \SI{300}{\mA
      \hour} battery?
    \begin{solution}
    \end{solution}
  \item What is the typical \(V_{DD}\) power consumptiono in standby
    mode with all features turned off?  How long could the chip remain
    in standby using a \SI{300}{\mA \hour} battery?
    \begin{solution}
    \end{solution}
  \item What is the range of ambient temperatures over which the
    microontroller will work reliably?
    \begin{solution}
    \end{solution}
  \item What is \(V_{IL}\) and \(V_{IH}\) for a generic digital I/O
    pin?
    \begin{solution}
    \end{solution}
  \item What are \(V_{OL}\) and \(V_{OH}\) for a digital CMOS I/O pin,
    assuming a maximum output current of \SI{8}{\mA}?
    \begin{solution}
    \end{solution}
  \item If you use an I/O pin to drive an LED, what is the maximum
    current you can expect to provide?  What resistor should you
    choose to achieve that current?
    \begin{solution}
    \end{solution}
  \item What is the maximum input leakage current for a pin, assuming
    the input voltage does not exceed \(V_{DD}\)?  If you were to
    connect a DIP switch to other pin with a pullup resistor, how
    large could the resistor be before the leakage causes the input
    pin to reach an invalid logic level?
    \begin{solution}
    \end{solution}
  \item How much Flash memory for programs is on the chip?
    \begin{solution}
    \end{solution}
  \item How much SRAM for data storage is on the chip?
    \begin{solution}
    \end{solution}
  \item How many bits of resolution does the ADC have?  How many
    external input channels can it read?  What is the maximum sampling
    rate?
    \begin{solution}
    \end{solution}
  \end{enumerate}

\item Impact on Society: Explain the impact of the C programming
  language on modern society.  When did C become widely used?  What
  languages were dominant before the rise of C, and how did C improve
  on them?  For what kinds of programming is C typically used today?
  Why does E85 teach C instead of another contemporary language
  (e.g. Python, C++, Java)?  Name at least one major drawback of the C
  language that has a concrete impact on geopolitics.
  \begin{solution}
  \end{solution}
\end{enumerate}

How long did you spend on this problem set?  This will not count
toward your grade but will help calibrate the workload.
\begin{solution}
\end{solution}
\end{document}