\documentclass{e85}

\lab{1}{Electrical Characteristics of Logic Gates}
\date{2019 February 4 (Monday)}
\author{}
\coauthor{}

\begin{document}

\begin{enumerate}
\item Please indicate how many hours you spent on this lab.  This will
  be helpful for calibrating the workload for next time the course is
  taught.  Include any suggestions you have for improving the lab.

  \begin{solution}

  \end{solution}

\item Gates, Switches, and LEDs
  \begin{enumerate}
  \item What resistor values did you choose?  Why?

    \begin{solution}

    \end{solution}

  \item Did your circuit function correctly?

    \begin{solution}

    \end{solution}
  \end{enumerate}

\item Transistor-level Inverter
  \begin{enumerate}
  \item Plot of VTC.

    \begin{solution}

    \end{solution}

  \item Input and output logic levels.

    \begin{solution}

    \end{solution}

  \item High and low noise margins.

    \begin{solution}

    \end{solution}
  \end{enumerate}

\item Ring oscillator

  \begin{enumerate}
  \item Photo of oscilloscope trace of switching output, annotated
    with the period and frequency.

    \begin{solution}

    \end{solution}

  \item Computer the average delay of a single inverter from the ring.

    \begin{solution}

    \end{solution}

  \item Why does the frequency change when you touch the wires?

    \begin{solution}

    \end{solution}

  \item Measured power consumption for both the ring oscillator and
    the powered quiescent chip.

    \begin{solution}

    \end{solution}
  \end{enumerate}

\item Full adder
  \begin{enumerate}
  \item Truth table.

    \begin{solution}

    \end{solution}

  \item Schematic.

    \begin{solution}

    \end{solution}

  \item Do your measured outputs match your truth table in all eight
    cases?

    \begin{solution}

    \end{solution}
  \end{enumerate}
\end{enumerate}

Please indicate any bugs you found in this lab manual, or any
suggestions you would have to improve the lab.
\begin{solution}

\end{solution}

\end{document}