\documentclass{ps}

\ps{9}
\date{2019}
\author{}
\coauthor{}

\begin{document}
\begin{enumerate}
\item Suppose the RegW signal in a single-cycle ARM processor has a
  \emph{stuck-at-1 fault} (e.g. the signal is always 1).  Which
  instructions would malfunction, and why?

  \begin{solution}
  \end{solution}

\item Modify the single-cycle ARM processor to implement the LSR
  instruction with a shamt5 immediate shift amount.  Mark up copies of
  the controller, main decoder, ALU decoder, and datapath (attached)
  to handle the new instruction as simply as possible.  Name any
  control signals you need to add.

  \begin{solution}
  \end{solution}

\item Modify the single-cycle ARM processor to implement the TST
  instruction.  Mark up the Verilog (attached) to implement your
  changes as simply as possible.

  \begin{solution}
  \end{solution}

\item Alyssa P. Hacker is a crack circuit designer.  She offers to
  speed up one of the functional units in Table 7.5 by
  \SI{50}{\percent} (e.g. cut the delay in half) to improve the
  overall performance of the single-cycle processor.  Which unit
  should she optimize, and by what percentage will the execution time
  improve?

  \begin{solution}
  \end{solution}

\item Impact on Society: Pick a phone or tablet that you or a friend
  uses that has one or more ARM processors inside.  Look up what
  processors are inside.  What company designed the microarchitecture?
  What company designed the chip?  What is the maximum clock
  frequency?  Does the processor implement the 32-bit (ARMv7) or
  64-bit (ARMv8) instruction set?

  \begin{solution}
  \end{solution}
\end{enumerate}

How long did you spend on this problem set?  This will not count
toward your grade but will help calibrate the workload.
\begin{solution}
\end{solution}
\end{document}