\documentclass{ps}

\ps{8}
\date{2019}
\author{}
\coauthor{}

\begin{document}
\begin{enumerate}
\item Assembly Language Programming

  Translate the following code snippet into ARM assembly language.

  \inputminted{c}{code/assembly-language-programming.c}

  \begin{solution}
  \end{solution}

\item Writing a Function in Assembly Language

  Do Exercise 6.25(a) from the textbook.
  \begin{description}
  \item[6.25] The high-level function \mintinline{c}|strcpy| copies
    the character string \mintinline{c}|src| to the character string
    \mintinline{c}|dst|.

    \inputminted{c}{code/writing-a-function-in-assembly-language.c}

    \begin{enumerate}[label=(\alph*)]
    \item Implement the \mintinline{c}|strcpy| function in ARM
      assembly code.  Use R4 for \mintinline{c}|i|.

      \begin{solution}
      \end{solution}
    \end{enumerate}
  \end{description}

\item Assembly Language to Machine Language

  Translate the following assembly language code to ARM machine
  language:

  \inputminted{text}{code/assembly-language-to-machine-language.arm}


  \begin{solution}
  \end{solution}

\item Machine Language to Assembly Language

  Translate the following machine language code to ARM assembly
  language:

  \inputminted{text}{code/machine-language-to-assembly-language}

  \begin{solution}
  \end{solution}

\item Impact on Society: ARM typically collects a royalty of 1--2\% of
  the selling price of a chip that includes one or more ARM
  processors.  Suppose you design your own ARM-compatible processor
  from scratch and put it on a chip that you sell.  Can ARM demand
  royalties?  If so, on what grounds wouldd their demand be
  enforceable in court?

  \begin{solution}
  \end{solution}
\end{enumerate}

How long did you spend on this problem set?  This will not count
toward your grade but will help calibrate the workload.
\begin{solution}
\end{solution}
\end{document}
